Centralizers of higher enveloping algebras and their large $N$ limits

### 2019-04-22 frame.tex
test of git
twisted

>>>>

\begin{rmk}
We briefly remark on a natural modification of the prefactorization algebra $\Sym(\cC_A)$. 
For simplicity, suppose $A$ is an ordinary (non dg) algebra, and let $\chi \in \Cyc^m(A, A^\vee)$ be a cyclic {\em cocycle} of degree $m$.
Consider, for each open $U \subset \RR^n$ the cochain complex
\[
\Tilde{\cC}_{A,\chi} (U) = \left(\Cyc_*(A \tensor \Omega^*_c(U))[1] \oplus \CC \cdot K , \d_{\rm Cyc} + K \cdot \chi \right) 
\]
where $K$ is a formal parameter of degree $-m+n+1$.
Also, $\d_{\rm Cyc}$ is the cyclic differential and $\chi$ is defined on $m$-chains by the pairing between cyclic chains and cochains, together with integration along $U$:
\[
\chi (\alpha_1 \tensor \cdots \tensor \alpha_m) = \int_U \<\chi, \alpha_1 \tensor \cdots \tensor \alpha_m\> .
\]
The differential is extended to the entire cochain complex by the graded Leibniz rule. 
By similar arguments as above, the assignment $U \subset \Tilde{\cC}_{A, \chi}$ is a precosheaf of cochain complexes and $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ is a prefactorization algebra. 
As a precosheaf of graded vectors spaces one has $\Tilde{\cC}_{A, \chi} = \cC_A \oplus \ul{\CC}[m-n-1]$, where $\ul{\CC}$ is the constant precosheaf, so that we may think of $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ as a twisted version of $\Sym(\cC_A)$. 
These types of twisted \brian{what to say? check my degrees!}
\end{rmk}
